\thesistitle

### 2019-07-16 sections/clonerefactor.tex
Removing redundant clone classes

>>>>

\subsubsection{Conceptual method of removing redundant clone classes}
Using the method described in the this section, we find redundant clones. We remove these clones if they are a subset of an existant clone. We define the subset relation between clones as displayed as follows:

\begin{equation}\label{eq:subset}
C_1 \subseteq C_2 \iff \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
\end{equation}

Where \textit{C} refers to a clone class (a set of clone instances), \textit{i} refers to a clone instance, \textit{F} is the file in which a clone instance is located and \textit{R} is the range of tokens that a clone instance spans. For each clone added, we remove all existing clones that are a subset of the newly added clone:

\begin{equation}\label{eq:removeall}
\text{For each new clone }C_{new}\text{ found, remove all clones in }(C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S)
\end{equation}

Where \textit{S} is the set of all clone classes that are found up in until this point. Likewise, we should not add the new clone to our list of clones if its a subset of an existing clone. Because of that, we check for each clone added whether there exists a clone of which the newly added clone is a subset:

\begin{equation}\label{eq:removeall}
\text{For each new clone }C_{new}\text{ found, only add it to }S \text{ iff } (C_{new} \subseteq C_{existing}\text{ }|\text{ }C_{existing} \in S)
\end{equation}
